intro

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated hypotheses

* H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) The majority of participants re-uses the strategy that was least effortful for them.

@@

* H4a) Subjective effort negatively predicts SVs of ER strategies.
* H4b) Subjective arousal negatively predicts SVs of ER strategies.
* H4c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
* H4d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.

* H5a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF *corrugator* and *levator* activity).

@@

* H6a) The higher the SV, the more likely the respective strategy is chosen.
* H6b) SVs are lower and decline stronger when ER flexibility is lower.

>>>>

* H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H5b) The majority of participants re-uses the strategy that was least effortful for them.

@@

* H5a) Subjective effort (effort ratings) negatively predicts SVs of ER strategies.
* H5b) Subjective arousal (arousal ratings) negatively predicts SVs of ER strategies.
* H5c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
* H5d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.

* H6a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF *corrugator* and *levator* activity).

@@

* H7a) The higher the SV, the more likely the respective strategy is chosen.
* H7b) SVs are lower and decline stronger when ER flexibility is lower.
